### 2022-05-22 doc/src/VSLevel.tex
Remove CSRs that set/clear an IMSIC interrupt file bit by number

As introduced in Chapter~\ref{ch:CSRs}, several hypervisor and VS CSRs
are added:  \z{hvien}, \z{hvictl}, \z{hviprio1}, \z{hviprio2},
\z{vsiselect}, \z{vsireg}, \z{vstopi}, \z{vsseteipnum},
\z{vsclreipnum}, \z{vsseteienum}, \z{vsclreienum}, and \z{vstopei}.
For RV32, the following ``high-half'' CSR partners are also added:
\z{hidelegh}, \z{hvienh}, \z{hviph}, \z{hviprio1h}, \z{hviprio2h},
\z{vsiph}, and \z{vsieh}.
As always, when executing in \mbox{VS-mode} or \mbox{VU-mode}, the
VS CSRs substitute for the corresponding supervisor CSRs.

@@

When \z{hstatus}.VGEIN is the valid number of a guest interrupt
file, values of \z{vsiselect} in the range \z{0x70}--\z{0xFF} select
registers of this guest interrupt file, just as values of \z{siselect}
in the same range select registers of the IMSIC's true supervisor-level
interrupt file.
The registers of an interrupt file that are accessed indirectly through
\z{vsiselect} and \z{vsireg} are documented in Chapter~\ref{ch:IMSIC}
on the IMSIC, along with the effects of accessing CSRs \z{vsseteipnum},
\z{vsclreipnum}, \z{vsseteienum}, \z{vsclreienum}, and \z{vstopei}.
Because all IMSIC interrupt files act identically, the guest interrupt
file that a virtual hart accesses through CSRs \z{siselect}, \z{sireg},
\z{sseteipnum}, \z{sclreipnum}, \z{sseteienum}, \z{sclreienum},
and \z{stopei} is indistinguishable from a true supervisor-level
interrupt file as seen from \mbox{S-mode} (or \mbox{HS-mode}).

@@

When a virtual hart appears to have an IMSIC because a guest interrupt
file is assigned to it, all external interrupts, real or emulated,
destined for the virtual hart must go through this perceived IMSIC.
A hypervisor can easily inject an emulated external interrupt into the
guest interrupt file selected by \z{hstatus}.VGEIN simply by writing to
CSR \z{vsseteipnum}.
When a virtual hart has a guest interrupt file, there is no reason
for a hypervisor to set bit VSEIP in CSR \z{hvip}, as this method
of asserting a VS-level external interrupt is more trouble than just
writing to \z{vsseteipnum} to set a specific interrupt-pending bit in
the guest interrupt file.

>>>>

As introduced in Chapter~\ref{ch:CSRs}, several hypervisor and VS CSRs
are added:  \z{hvien}, \z{hvictl}, \z{hviprio1}, \z{hviprio2},
\z{vsiselect}, \z{vsireg}, \z{vstopei}, and \z{vstopi}.
For RV32, the following ``high-half'' CSR partners are also added:
\z{hidelegh}, \z{hvienh}, \z{hviph}, \z{hviprio1h}, \z{hviprio2h},
\z{vsiph}, and \z{vsieh}.
As always, when executing in \mbox{VS-mode} or \mbox{VU-mode}, the
VS CSRs substitute for the corresponding supervisor CSRs.

@@

When \z{hstatus}.VGEIN is the valid number of a guest interrupt
file, values of \z{vsiselect} in the range \z{0x70}--\z{0xFF} select
registers of this guest interrupt file, just as values of \z{siselect}
in the same range select registers of the IMSIC's true supervisor-level
interrupt file.
The registers of an interrupt file that are accessed indirectly through
\z{vsiselect} and \z{vsireg} are documented in Chapter~\ref{ch:IMSIC}
on the IMSIC, along with IMSIC-only CSR \z{vstopei}.
Because all IMSIC interrupt files act identically, the guest interrupt
file that a virtual hart accesses through CSRs \z{siselect}, \z{sireg},
and \z{stopei} is indistinguishable from a true supervisor-level
interrupt file as seen from \mbox{S-mode} (or \mbox{HS-mode}).

@@

When a virtual hart appears to have an IMSIC because a guest interrupt
file is assigned to it, all external interrupts, real or emulated,
destined for the virtual hart must go through this perceived IMSIC.
A hypervisor can easily inject an emulated external interrupt into the
guest interrupt file selected by \z{hstatus}.VGEIN
by setting a bit in the interrupt-pending array
indirectly accessed through \z{vsiselect} and \z{vsireg}.
When a virtual hart has a guest interrupt file, a hypervisor
is not normally expected to set bit VSEIP in CSR \z{hvip}.
